%% part4
\MinParskip{}

\section{The EWM-TOPSIS Model}

\subsection{Indicators of the Model}
We selected 9 cities as evaluation objects. As the night-time light intensity directly reflects the extent of light pollution, so it is regarded as the direct evaluation indicator, and we chose 9 indirect indicators as evaluation indicator variables to evaluate the night light level of the city. 
The value of the j-th index variable of the i-th city evaluated is $a_{ij}$, building a matrix $A=(a_{ij})_{9\times9}$.

The eight indicators we selected are population density, night-time electricity consumption, per capita GDP, regional industrial structure, regional average working hours, the last bus time of public transport, night life index, limiting magnitude, etc. Among these indicators, only the limiting magnitude is an objective indicator and cannot be changed.

To explain the selection of indicators, We divide the indicators into two categories. One is the benefit-attributed indicators. The larger the data index, the higher the night-time light intensity. The other is the cost-attributed indicators. The smaller the data index, the higher the night-time light intensity.

For the benefit-attributed indicators, there are 6 indicators which are listed below.

\begin{enumerate}
    \item \textbf{Population density}. With the increase of population density in a region, the illumination demand of this region's public space also increases, thus increasing the night-time light intensity.
 
    \item \textbf{Night-time electricity consumption}. A large part of night-time electricity consumption is used for lighting, so it can also reflect the night-time light intensity to a certain extent, which is a benefit data. 
     
    \item \textbf{GDP per capita}. GDP per capita reflects the degree of local development. The more developed and prosperous the region, the more shopping malls and high-rise buildings in prosperous areas. And we believe the LED lights in shopping malls and the glass curtain walls of high-rise buildings lead to an increase in night-time light intensity, which may lead to the light pollution.
     
    \item \textbf{Regional industrial structure}. The demand for illumination in various industries is different. The primary industry has little demand for light. Some industries in the secondary industry have requirements for light, and the tertiary industry service industry is extremely dependent on light to attract customers. So the industrial structure also has an impact on the local night-time light intensity, and we believe that the more the proportion of the tertiary industry, the higher the nighttime light intensity is. 
     
    \item \textbf{Nightlife index}. Nightlife is a collective term for entertainment that is available and generally more popular from the late evening into the early hours of the morning. As long as nightlife prevails, the lighting demand increases. The higher the nightlife index of a region, the higher the nighttime light level, which belongs to the benefit data.
    
    \item \textbf{The last bus time of public transport}. The operation guarantee condition of ground public transportation is lighting, so the lighting will naturally increase during the traffic operation time. And also to some extent, the last subway train time is connected with the night-time living. The later the last bus is, the higher the night-time lighting level will be, so it belongs to the benefit data.
\end{enumerate}

For the cost-attributed indicators, there are 2 indicators which are listed below.
\begin{enumerate}
    \item \textbf{The average working hours in the region}. The earlier people leave work, the earlier the end of the evening commute. So the demand for high-beam lights will become less, and the demand for night lighting time will become less, so it will affect the level of night-time lighting.
    
    \item \textbf{Limit magnitude}. Limit magnitude refers to the darkest magnitude that can be observed through a telescope. The higher the limit magnitude that can be seen, the lower the brightness on the ground, that is equal to lower level of illumination at night, so it belongs to the cost data.
\end{enumerate}



\subsection{The Entropy Weight Method (EWM) }
We use the Entropy Weight Method (EWM) to get the weight of indicators. The Entropy Weight Method is an object weighting method, which uses the information entropy idea for reference. It is used to determine the relative weights of different criteria in a decision-making process. It determines the weight of the indicators by calculating the information entropy of the index, according to the impact of the relative change of the index on the overall system.

In other words, the weight of each indicator is given according to the difference degree of the indicator value, and the corresponding weight of each indicator is obtained. The indicator with relatively large change degree has larger weight. 

The greater the entropy, the more chaotic the system is, the less information it carries and the less weight it has. Otherwise, the higher the entropy, the more orderly the system is, the more information it carries, and the greater the weight is.

The first step of the Entropy Weight Method is the standardization of measured values. The standardized value of the jth index in the ith sample is denoted as $p_{ij}$, and its calculation method is as follows:$$p_{ij}=\frac{a_{ij}}{\sum_{i=1}^na_{ij}},i=1,2\cdots,,9,j=1,2,\cdots,8$$

Secondly, in the EWM, the entropy value $e_i$ of the jth index is defined as:$$e_j=-\frac{1}{ln(9)}\sum_{i=1}^np_{ij}ln(p_{ij}),j=1,2,\cdots,8$$
The range of entropy value $e_j$ is [0, 1]. The larger the $e_j$ is, the greater the differentiation degree of index j is, and more information can be derived. Hence, higher weight should be given to the index. 

Finally, the calculation method of weight is:$$w_j=\frac{1-e_j}{\sum_{j=1}^me_j},j=1,2,\cdots,8$$

Through the three steps, we can easily get the weight of each indicator.


\subsection{The TOPSIS Method}
/*NOTDONENOTDONE

The Technique for Order of Preference by Similarity to Ideal Solution (TOPSIS) is a multi-criteria decision-making method that is used to determine the best option from a set of alternatives based on multiple criteria. 

First of all, we use Min-Max normalization to process the data.

For the benefit-attributed data,
$$b_{ij}=\frac{a_{ij}-a_j^{min}}{a_j^{max}-a_j^{min}}$$

And for the cost-attributed data,
$$b_{ij}=\frac{a_{j}^{max}-a_{ij}}{a_j^{max}-a_j^{min}}$$

All these data from the normalized matrix $B$. We then multiply each value in a column with the corresponding weight given, and get weighted-normalised decision matrix, which $$C=W*B$$

Secondly, calculating the ideal best and the ideal worst. Now we need to calculate Euclidean distance for elements in all rows from the ideal best and the ideal worst. Here, $s_i^*$ is the best distance calculated on the i-th row, where $b_{ij}$ is element value and $C_i^{*}$ is the ideal best for that column. Similarly, we can find $s_i^0$, which is the worst distance calculated on the i-th row.

// insert a table

Finally, calculating Topsis Score and Ranking. Now we have distance positive and distance negative, calculate the Topsis score for each row based on them in the end.

NOTDONENOTDONE*/


\subsection{Application of the Model on the Four Locations}


\subsubsection{A Protected Land Location: }

\subsubsection{A Rural Community: }

\subsubsection{A Suburban Community: }

\subsubsection{An Urban Community: }

