%% part2
\MinParskip{}
\section{Assumptions and Justifications} 
To simplify the problem, we make the following basic assumptions.

\begin{itemize}
    \item Assume that all the light pollution is from night-time light, so we just need to consider night-time light intensity.  

    \textbf{Justifications: }According to the Wikipedia\cite{wiki}, the definition of light pollution is the presence of anthropogenic artificial light in otherwise dark conditions. 

    \item Citizens will not reduce the basic consumption of living illumination for the purpose of reducing light pollution.
    
    \textbf{Justifications: }To simplify the problem, we didn't take people's awareness of light pollution into account.

    \item Precipitation occurs in the day and night with equal probability.
    
    \textbf{Justifications: }As we use year precipitation to evaluate the cloudness of one location, and the light pollution occurs in the night-time, only rainy at night that the precipitation data is valid. So that the year precipitation can be comparable.

    \item Night-time light intensity is closely related with economics.
    
    \textbf{Justifications: }According to fractional logit models\cite{GALLAWAY2010658}, both population and GDP are significant explanatory variables, similar to other types of pollution. 
\end{itemize}

\section{Notations}
Symbols used and their definitions are defined below(Table 1).
\begin{table}[H] \centering
    \caption{Notations of symbols}
    \begin{tabular}{ccl}
        \toprule
        Symbol & Description\\ \hline
        $a_{ij}$ & The value of the j-th indicator of the i-th city to be evaluated. \\
        $A=(a_{ij})_{i\times j}$ & Data matrix composed by $a_{ij}$. \\
        $p_{ij}$ & The proportion of the i-th evaluation objective to the j-th indicator. \\
        $e_j$ & The entropy value of the j-th indicator. \\
        $w_j$ & The weight of the j-th indicator. \\
        $b_{ij}$ & The data from $a_{ij}$ after standard 0-1 transformation.\\
        $B=(b_{ij})_{i\times j}$ & The decision matrix composed by $b_{ij}$ after processing.\\
        $C=W*B$ & The weighted-normalised decision matrix. \\
        $C_i$ & The i-th roll of the $C$ matrix. \\
        $C^*=[b_1^{max},b_2^{max},\cdots,b_j^{max}]$ & The positive ideal solution. \\
        $C^*=[b_1^{min},b_2^{min},\cdots,b_j^{min}]$ & The negative ideal solution. \\
        $s_i^*$ & The distance from $C_i$ to the positive ideal solution. \\
        $s_i^0$ & The distance from $C_i$ to the negative ideal solution. \\
        $f_i$ & The night-time light intensity of the i-th city. \\
        \bottomrule
    \end{tabular}
\end{table}