%% part1
\MinParskip{}

\section{Basic Introduction}

\subsection{Background}
In 2017, the worst hurricane to ever hit the United States territory of Puerto Rico left the island with severe damage and caused over 2900 fatalities. The combined destructive power of the hurricane's storm surge and wave action produced extensive damage to buildings, homes, and roads, particularly along the east and southeast coast of Puerto Rico. The storm, with its fierce winds and heavy rain, knocked down 80 percent of Puerto Rico's utility poles and all transmission lines, resulting in loss of power to essentially all of the island's 3.4 million residents. In addition, the storm damaged or destroyed the majority of the island's cellular communication networks. The electrical power and cell service outages lasted for months across much of the island, and longer in some locations. Widespread flooding blocked and damaged many highways and roads across the island, making it nearly impossible for emergency services ground vehicles to plan and navigate their routes. The full extent of the damage in Puerto Rico remained unclear for some time; dozens of areas were isolated and without communication. Demands for medical supplies, lifesaving equipment, and treatment strained health-care clinics, hospital emergency rooms, and non-governmental organizations' (NGOs) relief operations. Demand for medical care continued to surge for some time as the chronically ill turned to hospitals and temporary shelters for care.

\subsection{Literature Review}


\subsection{Problem Restatement}
\begin{itemize}
    \item Design and minimize the cost of a drone fleet, and also the associated packing configuration.
    \item When designing a drone fleet, take consideration of both video and medical package capability.
    \item Route designing and drone payload packing configurations.
    \item Write a 1-2 page memo to the CEO of HELP, Inc.
\end{itemize}

\subsection{Our works}


\subsection{Assumptions and Justifications} 

\begin{itemize}
    \item Assume that 
\end{itemize}

\textbf{Justifications: }

\begin{itemize}
    \item Assume that 
\end{itemize}

\textbf{Justifications: }


\subsection{Notations}
The mostly used symbols and their definitions are defined (Table 1), and more symbols will be defined later in the text. 
\begin{table}[h] \centering
    \caption{Notations of symbols}
    \begin{tabular}{ccl}
        \toprule
        Symbol & Data Type & Description\\ \hline
        $D_{ik}$ & Boolean & The i-th drone will heading for the k-th place. \\
        $Y_{im}$ & Boolean & The i-th drone uses the m-th type of drone. \\
        $V_i$ & Boolean & The i-th drone has video capability. \\
        $C_{imk}$ & Boolean & The i-th drone carries the m-th type of package to the\\ & & k-th place.\\
        $T_i$ & Two-dimensional Array & The possible combination of the i-th drone to carry the\\ & &packages.\\
        $T_i[j][m]$ & Interger & The number of the m-th type of package in the j-th\\ & & combination of the i-th drone.\\
        $X_m$ & Two-dimensional Array & The combination of different medical packages in the\\ & & m-th type of package. \\
        $N_k$ & Vector & The number of the medical packages needed in the k-th \\ & & place.\\
        \bottomrule
    \end{tabular}
\end{table}



